---
title: "Visualizing both a categorical and a numeric variable"
output: github_document
---

We are requested to answer:

    1. How does average box-office revenue compare across raings?
    2. How similar are the spreads of box-office revenue across ratings?
    3. How do their shapes compare?
    
*Bivariate visualizations for bith qualitiative and quantitiative bivariate variable*

## Setting up environment

```{r}
movies <- read.csv("../data/Movies.csv")
main_label <- "Average Box-Office Revenue by Rating"
rating_label <- "Rating"
box_office_label <- "Box Office ($M)"
library(lattice)
```

Install dplyr library `install.packages("dplyr")`

```{r}
library("dplyr")
```


## Plots


Create table of average box office by rating

```{r}
average  <- movies %>% 
  select(Rating, Box.Office) %>%
  group_by(Rating) %>%
  summarize(Box.Office = mean(Box.Office)) %>%
  as.data.frame()

print(average)
```

### Bivariate Bar Chart

```{r}
barchart(
  x = Box.Office ~ Rating,
  data = average,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label)
```

### Bivariate box plot

```{r}
main_label <- "Box Office Revenue by Rating"
bwplot(
  x = Box.Office ~ Rating,
  data = movies,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label)
```

### Notched Box Plot

```{r}
bwplot(
  x = Box.Office ~ Rating,
  data = movies,
  notch = TRUE,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label)
```

### Violing plot

```{r}
bwplot(
  x = Box.Office ~ Rating,
  data = movies,
  panel = panel.violin,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label)
```


