---
title: "Visualizing one categorical Variable - Base"
output: github_document
---

## Environment setup 

Set working directory (no needed if working on R project)  
`setwd("path")`  

Load movie data from CSV file
```{r}
movies <- read.csv("../data/Movies.csv")
```

Peek at the data
```{r}
head(movies)
```

## Univariate visualization for a qualitative variable

Create a frequency bar chart of ratings, *the chart internally resolve to display data as bar chart*
```{r}
plot(
  x = movies$Rating,
  main = "Count of Movies by Rating",
  xlab = "Raiting",
  ylab = "Count of Movies"
)
```

Create a horizontal frecuency chart of ratings
```{r}
plot(
  x= movies$Rating,
  horiz = TRUE,
  main ="Count of Movies by Rating",
  xlab = "Count of Movies",
  ylab = "Rating"
)
```

Create a Cleveland dot plot, *this is pretty much the same than the bar chart*

```{r}
dotchart(
  x = table(movies$Rating),
  pch = 16,
  main = "Count of Movies by Rating",
  xlab = "Count of Movies",
  ylab = "Rating"
)
```

Create a Pie chart of ratings
```{r}
pie(
  x = table(movies$Rating),
  main = "Count of Movies by Rating")
```

Create pie chart of awards

```{r}
pie(
  x = table(movies$Awards),
  clockwise = TRUE,
  main="Proportion of Movies that Won Awards"
)
```
