---
title: "Data Visualization - Quantitative Bivariate Analysis"
output: github_document
---

# Data Load

Let's start by taking a look to our current dataset


```{r}
library(tidyverse)
library(dslabs)
library(lattice)
library(lubridate)

load("rda/apps_dataset.rda")
load("rda/apps_categories_dataset.rda")
load("rda/apps_genres_dataset.rda")
load("rda/apps_versions_dataset.rda")
ds_theme_set()
```

# Data Visualization

## Quantitative Bivariate Analysis

Quantitative Features:

    * Ratings
    * Reviews
    * Size (Numeric)
    * Price
    * Last Updated
    * Installs (Numeric)

### Ratings vs Reviews


#### Scatterplot

```{r}
title <- "Reviews vs Rating"
x_lab <- "Rating"
y_lab <- "Review"
z_lab <- "Density"
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x=Rating, y=Reviews)) +
  geom_point() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```


with linear regression, even we already know there is no correlation between those features.

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = Reviews)) +
  geom_point() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  geom_smooth(method = "lm")


```




#### Binned Frequency Heatmap

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x= Rating, y = Reviews)) +
  stat_bin2d() +
  ggtitle(title)+
  xlab(x_lab) +
  ylab(y_lab)

```



#### Hexagonal Binned Frequency Heatmap

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x=Rating, y=Reviews)) +
  stat_binhex() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```


#### Countour Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = Reviews)) +
  geom_density2d() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```


#### Level Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y =  Reviews)) +
  stat_density2d(aes(fill = ..level..), geom= "polygon") +
  ggtitle(title) +
  xlab(x_lab)+
  ylab(y_lab)
```


#### Mesh Plot

Creating the 2D kernel

```{r}
library(MASS)

temp_data <-
  apps_versions_dataset %>%
  filter(!is.na(Rating))
  

density2d <- kde2d(
  x = temp_data$Rating,
  y = temp_data$Reviews,
  n = 50)

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)

head(grid)

```


```{r}

grid %>%
  wireframe(
  x = z ~ x * y ,
  main = title,
  xlab= x_lab,
  ylab = y_lab,
  zlab = z_lab
)
```


#### Surface Plot

for the sake of practice, I am repeating the process to create the grid object

```{r}

temp_data <- apps_versions_dataset%>%
  filter(!is.na(Rating)) 

density2d <- kde2d(
  x =  temp_data$Rating,
  y = temp_data$Reviews,
  n = 50)

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z = as.vector(density2d$z)

head(grid)

```

```{r}
grid %>%
  wireframe(
    x = z ~ x * y,
    drape = TRUE,
    main = title,
    xlab = x_lab,
    ylab = y_lab,
    zlab = z_lab)
```


### Ratings vs Size

#### Scatterplot

We can see there is no correlation between App Rating and size

```{r}
title <- "Ratings vs Size"
y_lab <- "Size"

apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = SizeNumeric)) +
  geom_point() +
  ggtitle(title)
```

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = SizeNumeric)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
  
```


#### Binned Frequency Heatmap

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x=Rating, y = SizeNumeric)) +
  stat_bin2d() +
  ggtitle (title) +
  xlab(x_lab) +
  ylab(y_lab)
```



#### Hexagonal Binned Frequency Heatmap

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = SizeNumeric)) +
  stat_binhex() +
  ggtitle(title)+
  xlab(x_lab)+
  ylab(y_lab)

```


#### Countour Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = SizeNumeric)) +
  geom_density2d() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)

```


#### Level Plot


```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  ggplot(aes(x = Rating, y = SizeNumeric)) +
  stat_density2d(aes(fill = ..level..), geom = "polygon") +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```


#### Mesh Plot

```{r}
temp_data <- apps_versions_dataset %>% filter(!is.na(Rating))

density2d <- kde2d(
  x = temp_data$Rating,
  y = temp_data$SizeNumeric,
  n = 50)

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)

grid %>%
  wireframe(
    x = z ~ x * y,
    main = title,
    xlab = x_lab,
    ylab = y_lab,
    zlab = z_lab)
```


#### Surface Plot

```{r}

temp_data <- apps_versions_dataset %>%
  filter(!is.na(Rating))
  
density2d <- kde2d(
  x = temp_data$Rating,
  y = temp_data$SizeNumeric,
  n = 50)  

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)

grid %>%
  wireframe(
    x = z ~ x * y, 
    drape = TRUE,
    main = title,
    xlab = x_lab,
    ylab = y_lab,
    zlab = z_lab)
```



### Ratings vs Price

#### Scatterplot


```{r}
title <- "Rating vs Price"
x_lab <- "Rating"
y_lab <- "Price"

apps_versions_dataset %>%
  filter(!is.na(Rating) & Type == "Paid") %>%
  ggplot(aes(x= Rating, y = PriceNumeric)) +
  geom_point() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```


```{r}
apps_versions_dataset %>% 
  filter(!is.na(Rating) & Type == "Paid") %>%
  ggplot(aes(x = Rating, y = PriceNumeric)) +
  geom_point() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  geom_smooth(method = "lm")
```
Taking a look at the graph above, one can think about some correlation between low price better rating... but this may be an example of correlation is not causation...

#### Binned Frequency Heatmap

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating) & Type == "Paid") %>%
  ggplot(aes(x = Rating, y = PriceNumeric)) +
  stat_bin2d() +
  ggtitle(title) +
  xlab (x_lab) +
  ylab (y_lab)
  
```



#### Hexagonal Binned Frequency Heatmap

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating) & Type == "Paid") %>%
  ggplot(aes(x = Rating, y = PriceNumeric)) +
  stat_binhex() +
  ggtitle(title) +
  xlab (x_lab) +
  ylab (y_lab)
```



#### Countour Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating) & Type == "Paid")  %>%
  ggplot(aes(x = Rating, y = PriceNumeric)) +
  geom_density2d() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```



#### Level Plot

```{r}
apps_versions_dataset %>%
  filter(!is.na(Rating) & Type == "Paid")  %>%
  ggplot(aes(x = Rating, y = PriceNumeric)) +
  stat_density2d(aes(fill = ..level..), geom = "polygon") +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
```


#### Mesh Plot

```{r}
temp_data <- apps_versions_dataset %>% filter(!is.na(Rating) & Type == "Paid")

density2d <- kde2d(
  x = temp_data$Rating,
  y = temp_data$PriceNumeric,
  n = 50)

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)


grid$z <- as.vector(density2d$z)

grid %>% 
  wireframe(
  x = z ~ x * y,
  main = title,
  xlab = x_lab,
  ylab = y_lab,
  zlab = z_lab)

```


#### Surface Plot

```{r}
temp_data <- apps_versions_dataset %>% filter(!is.na(Rating) & Type == "Paid") 

density2d <- kde2d(
  x = temp_data$Rating,
  y = temp_data$PriceNumeric,
  n = 50)

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)

grid %>%
  wireframe(
    x = z ~ x * y,
    drape = TRUE,
    main = title,
    xlab = x_lab,
    ylab = y_lab,
    zlab = z_lab)

```


### Size vs Price

#### Scatterplot

```{r}
title <- "Size vs Price"
x_lab <- "Size"
y_lab <- "Price"

ggplot <- apps_versions_dataset %>%
  filter(Type == "Paid") %>%
  ggplot(aes(x = SizeNumeric, y = PriceNumeric)) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab)
  
  ggplot +
  geom_point()
  
```

#### Binned Frequency Heatmap

```{r}
  ggplot +
  stat_bin2d()
  
```

#### Hexagonal Binned Frequency Heatmap

```{r}
  ggplot + 
  stat_binhex()

```


#### Countour Plot

```{r}
ggplot +
  geom_density2d()
```


#### Level Plot

```{r}
ggplot +
  stat_density2d(aes(fill = ..level..) , geom = "polygon")
```


#### Mesh Plot


```{r}
temp_data <- apps_versions_dataset %>% filter(Type == "Paid")

density2d <- kde2d(
  x = temp_data$SizeNumeric,
  y = temp_data$PriceNumeric,
  n = 50)

grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)

grid %>%
  wireframe(
    x = z ~ x * y,
    main = title,
    xlab = x_lab,
    ylab = y_lab,
    zlab = z_lab)
```


#### Surface Plot

```{r}
grid %>%
  wireframe(
    x = z ~ x * y,
    main = title,
    xlab = x_lab,
    ylab = y_lab,
    zlab = z_lab,
    drape = TRUE
  )
```



### Ratings vs Last Updated

#### Step Chart

```{r}
title <- "Ratings by Year"
x_lab <- "Year"
y_lab <- "Rating"

temp_data <- apps_versions_dataset %>% 
  filter(!is.na(Rating) & !is.nan(Rating)) %>%
  mutate(Year.Month = round_date(Last.UpdatedDate, unit = "month")) %>%
  group_by(Year.Month) %>%
  summarize(Date =max(Year.Month),Max = max(Rating), Min = min(Rating),Mean = mean(Rating), n = n())
  
  
temp_data %>% 
  ggplot(aes(x = Date, y= Mean)) +
  geom_step() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  expand_limits(y = 0)

```


#### Line Chart

```{r}
temp_data %>%
  ggplot(aes(x = Date, y= Mean)) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  geom_line() +
  expand_limits(y = 0)
  
```


#### Area chart

```{r}
temp_data %>%
  ggplot(aes(x = Date, y= Mean)) +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  geom_area() +
  expand_limits(y = 0)

```


### Apps vs Last Updated

#### Step Chart

```{r}
title <- "Apps by Year"
y_lab <- "Apps"

temp_data <- apps_versions_dataset %>%
  mutate(Year.Month = round_date(Last.UpdatedDate, unit = "month")) %>%
  group_by(Year.Month)  %>%
  summarize(Date = max(Year.Month), Count = n())


temp_data %>%
  ggplot(aes(x = Date, y = Count)) +
  geom_step() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  expand_limits(y = 0)

```

#### Line Chart

```{r}
temp_data %>%
  ggplot(aes(x = Date, y = Count)) +
  geom_line() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  expand_limits(y = 0)
  
```


#### Area chart

```{r}
temp_data %>%
  ggplot(aes(x = Date, y = Count)) +
  geom_area() +
  ggtitle(title) +
  xlab(x_lab) +
  ylab(y_lab) +
  expand_limits(y = 0)
  
```