---
title: "Data Visualization - Quantitative Bivariate Analysis"
output: github_document
---

# Data Load

Let's start by taking a look to our current dataset


```{r}
library(tidyverse)
library(dslabs)
library(lattice)
library(lubridate)

load("rda/apps_dataset.rda")
load("rda/apps_categories_dataset.rda")
load("rda/apps_genres_dataset.rda")
load("rda/apps_versions_dataset.rda")
ds_theme_set()
```

# Data Visualization

## Quantitative Bivariate Analysis

Quantitative Features:

    * Ratings
    * Reviews
    * Size (Numeric)
    * Price


Qualitative Features:

    * Category
    * Installs (Install range)
    * Type (Free/Paid)
    * Content Rating
    * Genre


### Content Rating vs Reviews


#### Bivariate Bar Chart
```{r}

options(scipen = 999) # Disabling Scientific notation
ggplot <- apps_versions_dataset %>%
  ggplot(aes(x = Content.Rating, y = Reviews)) +
  ggtitle("Rating by Content Rating") +
  xlab("Content Rating") +
  ylab("Reviews")


ggplot +
  geom_bar(stat = "identity") 
  
```

#### Boxplot

```{r}

ggplot +
  geom_boxplot()

```


#### Notched Boxplot

```{r}

ggplot +
  geom_boxplot(notch = TRUE)

```



#### Violin Plot

```{r}
ggplot +
  geom_violin()
```


### Content Rating vs Price

#### Bivariate Bar Chart

```{r}
ggplot <-  apps_versions_dataset %>%
  filter(Type == "Paid") %>%
  ggplot(aes(x = Content.Rating, y = PriceNumeric)) +
  ggtitle("Price by Content Rating") +
  xlab("Content Rating") +
  ylab("Price")


ggplot +
  geom_bar(stat = "identity")
```

#### Box Plot

```{r}
ggplot +
  geom_boxplot()
```

Removing some outliers

```{r}
ggplot2 <-  apps_versions_dataset %>%
  filter(Type == "Paid" & PriceNumeric <= 50) %>%
  ggplot(aes(x = Content.Rating, y = PriceNumeric)) +
  ggtitle("Price by Content Rating") +
  xlab("Content Rating") +
  ylab("Price")
  
  ggplot2 +
    geom_boxplot()

```



#### Notched Box Plot

```{r}
ggplot +
  geom_boxplot(notch =  TRUE)
```

We remove some outliers

```{r}
ggplot2 +
  geom_boxplot(notch = TRUE)
```



#### Violin Plot

```{r}
ggplot +
  geom_violin()
```


### Type vs Reviews


#### Bivariate Bar Chart
```{r}
ggplot <- apps_versions_dataset %>%
  ggplot(aes(x = Type, y = Reviews)) +
  ggtitle("Reviews by Type") +
  xlab("Type") +
  ylab("Reviews")


ggplot +
  geom_bar(stat = "identity")
  
```

#### Box Plot

```{r}
ggplot +
  geom_boxplot()
```

#### Notched Box Plot

```{r}
ggplot +
  geom_boxplot(notch = TRUE)
```

#### Violin Plot

```{r}
ggplot +
  geom_violin()
```
