---
title: "Visualizing both a categorical and a numeric variable"
output: github_document
---

We are requested to answer:

    1. How does average box-office revenue compare across raings?
    2. How similar are the spreads of box-office revenue across ratings?
    3. How do their shapes compare?
    
*Bivariate visualizations for bith qualitiative and quantitiative bivariate variable*

## Setting up environment

```{r}
movies <- read.csv("../data/Movies.csv")
main_label <- "Average Box-Office Revenue by Rating"
rating_label <- "Rating"
box_office_label <- "Box Office ($M)"
```

## Plots

### Bivariate bar graph

```{r}
average <- tapply(
  movies$Box.Office,
  movies$Rating,
  mean)

print(average)
```

```{r}
barplot(
  height = average,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label
)
```



### Bivariate box plot

Create a bivariate box plot

```{r}

main_label <- "Box Office Revenue by Rating"
plot(
  x = movies$Rating,
  y = movies$Box.Office,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label)
```


### Notched boxplot

Create a notched box plot
```{r}
plot(
  x = movies$Rating,
  y = movies$Box.Office,
  notch = TRUE,
  main = main_label,
  xlab = rating_label,
  ylab = box_office_label)
```

### Violing plot

**There is no Violing plot on the base library**