---
title: "Visualizing both a categorical and a numeric variable"
output: github_document
---

We are requested to answer:

    1. How does average box-office revenue compare across raings?
    2. How similar are the spreads of box-office revenue across ratings?
    3. How do their shapes compare?
    
*Bivariate visualizations for bith qualitiative and quantitiative bivariate variable*

## Setting up environment

```{r}
movies <- read.csv("../data/Movies.csv")
main_label <- "Average Box-Office Revenue by Rating"
rating_label <- "Rating"
box_office_label <- "Box Office ($M)"
library(ggplot2)
library(dplyr)
```

## Plots
Create table of average box office by rating

```{r}
average  <- movies %>% 
  select(Rating, Box.Office) %>%
  group_by(Rating) %>%
  summarize(Box.Office = mean(Box.Office)) %>%
  as.data.frame()

print(average)
```

### Bivariate bar chart

```{r}
ggplot(
  data = average,
  aes(x =Rating, y = Box.Office)) +
  geom_bar(stat = "identity") +
  ggtitle(main_label) +
  xlab(rating_label) +
  ylab(box_office_label)
```

### Boxplot

```{r}
main_label <- "Box Office Revenue by Rating"
ggplot(
  data = movies,
  aes(x = Rating, y = Box.Office)) +
  geom_boxplot() +
  ggtitle(main_label) + 
  xlab(rating_label) +
  ylab(box_office_label)
```

### Notched boxplot

```{r}
main_label <- "Box Office Revenue by Rating"
ggplot(
  data = movies,
  aes(x = Rating, y = Box.Office)) +
  geom_boxplot(notch = TRUE) +
  ggtitle(main_label) + 
  xlab(rating_label) +
  ylab(box_office_label)

```

### Violin plot

```{r}
ggplot(
  data = movies,
  aes(x= Rating, y = Box.Office)) +
  geom_violin() +
  ggtitle(main_label) +
  xlab(rating_label) +
  ylab(box_office_label)
```

