---
title: "Visualizing Two Numeric Variables"
output: github_document
---

We are requested to answer these questions:

    1. How are runtime and box-office revenue related?
    2. Has the average box-office revenue changed over time?
    
    
*Bivariate Visualization for two quantitiative variables*
## Setting up environment

```{r}
library(lattice)
movies <- read.csv('../data/Movies.csv')
main_label <- "Runtime vs. Box Office Revenue"
runtime_in_minutes_label <- "Runtime (minutes)"
box_office_label <- "Box Office ($M)"
density_label <- "Density"
```

## Plots


### Scatter Plot
Create a scatterplot

```{r}
xyplot(
  x = Box.Office ~ Runtime,
  data = movies,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

#### Adding a regression line

```{r}
xyplot(
  x = Box.Office ~ Runtime,
  data = movies,
  type = c("p","r"), # p stands for points and r stands for regression
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

### Load hexbin library
```{r}
library(hexbin)
```

### Hexagonal binned frequency heatmap

Create hexagonal binned frequency heatmap

```{r}
hexbinplot(
  x = Box.Office ~ Runtime,
  data = movies,
  xbins = 30,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

### Grid from our 2D kernel density estimate

#### MASS Package

For the following plots we need to create a 2D kernel density estimate using MASS, to install it we execute `install.packages("MASS")`  

Now we load the library
```{r}
library(MASS)
```

Now create a 2D kernel density estimation

```{r}
density2d <- kde2d(
  x = movies$Runtime,
  y = movies$Box.Office,
  n = 50)
```


Create a grid from our 2D kernel density estimate, the data structure is a *data frame*

```{r}
grid <- expand.grid(
  x = density2d$x,
  y = density2d$y)

grid$z <- as.vector(density2d$z)
```

Display the data frame

```{r}
head(grid)
```

### Contour plot of density

Create a contour plot of density

```{r}
contourplot(
  x = z ~ x* y,
  data = grid,
  main = main_label,
  xlab = 
)
```


### Level plot of density

Create a level plot of density

```{r}
levelplot(
  x = z ~ x * y,
  data = grid,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```

### Mesh plot

Create mesh plot of density

```{r}
wireframe(
  x = z ~ x * y,
  data = grid,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label,
  zlab = density_label)
```

### Surface plot

Create surface plot of density

```{r}
wireframe(
  x = z ~ x * y,
  data = grid,
  drape = TRUE,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label,
  zlab = density_label)
```

### Load time series data

Load time series data
```{r}
timeSeries <- read.csv("../data/Timeseries.csv")
```

Display the time series data

```{r}
head(timeSeries)
```

### Step chart

Create a step chart

```{r}
xyplot(
  x = Box.Office ~ Year,
  data = timeSeries,
  type = 's',
  ylim = c(0,max(timeSeries$Box.Office)),
  main = "Average Box Office Revenue by Year",
  xlab = "Year",
  ylab = box_office_label)
```


### Line chart

Create a line chart

```{r}
 xyplot(
   x = Box.Office ~ Year,
   data = timeSeries,
   type = "l",
   ylim = c(0, max(timeSeries$Box.Office)),
   main = "Average Box Office Revenue by Year",
   xlab = "Year",
   ylab = box_office_label)
```

### Area chart

#### LatticeExtra library

We need to install "latticeExtra" library to create area charts.

Installation command `install.packages("latticeExtra")`

Loading the library
```{r}
library("latticeExtra")
```

Area Chart

```{r}
xyplot(
  x = Box.Office ~ Year,
  data = timeSeries,
  panel = panel.xyarea,
  ylim = c(0, max(timeSeries$Box.Office)),
  main = "Average Box Office Revenue by Year",
  xlab = "Year",
  ylab = box_office_label)
```
