---
title: "Comprehension Check: Generative Models"
output: github_document
---

## Q1
Create a dataset of samples from just cerebellum and hippocampus, two parts of the brain, and a predictor matrix with 10 randomly selected columns using the following code:

```{r}
library(dslabs)
library(caret)
library(tidyverse)
data("tissue_gene_expression")
      
set.seed(1993)
ind <- which(tissue_gene_expression$y %in% c("cerebellum", "hippocampus"))
y <- droplevels(tissue_gene_expression$y[ind])
x <- tissue_gene_expression$x[ind, ]
x <- x[, sample(ncol(x), 10)]

```

Use the train function to estimate the accuracy of LDA. For this question, use the entire tissue_gene_expression dataset: do not split it into training and test sets (understand this can lead to overfitting).

```{r}
train_lda <- train(x,y , method = "lda")
train_lda$results["Accuracy"]

```

Answer: Expected from course 0.871 (What I got 0.9804733)

What is the accuracy?


## Q2

In this case, LDA fits two 10-dimensional normal distributions. Look at the fitted model by looking at the finalModel component of the result of train. Notice there is a component called means that includes the estimated means of both distributions. Plot the mean vectors against each other and determine which predictors (genes) appear to be driving the algorithm.

```{r}
train_lda$finalModel
```

```{r}
t(train_lda$finalModel$means) %>% data.frame() %>%
	mutate(predictor_name = rownames(.)) %>%
	ggplot(aes(cerebellum, hippocampus, label = predictor_name)) +
	geom_point() +
	geom_text() +
	geom_abline()

```

Which TWO genes appear to be driving the algorithm?
Answer RAB1B & OAZ2


## Q3 
Repeat the exercise in Q1 with QDA.

Create a dataset of samples from just cerebellum and hippocampus, two parts of the brain, and a predictor matrix with 10 randomly selected columns using the following code:
```{r}
library(dslabs)      
library(caret)
data("tissue_gene_expression")
      
set.seed(1993)
ind <- which(tissue_gene_expression$y %in% c("cerebellum", "hippocampus"))
y <- droplevels(tissue_gene_expression$y[ind])
x <- tissue_gene_expression$x[ind, ]
x <- x[, sample(ncol(x), 10)]

```

Use the train function to estimate the accuracy of QDA. For this question, use the entire tissue_gene_expression dataset: do not split it into training and test sets (understand this can lead to overfitting).

```{r}
fit_qda <- train(x, y, method = "qda")
fit_qda$results["Accuracy"]
```

What is the accuracy?
Answer: expected 0.815, gotten 0.9256


## Q4
Which TWO genes drive the algorithm when using QDA instead of LDA?
```{r}
t(fit_qda$finalModel$means) %>% data.frame() %>%
	mutate(predictor_name = rownames(.)) %>%
	ggplot(aes(cerebellum, hippocampus, label = predictor_name)) +
	geom_point() +
	geom_text() +
	geom_abline()
```


Answer: 
RAB1B & OAZ2


## Q5
One thing we saw in the previous plots is that the values of the predictors correlate in both groups: some predictors are low in both groups and others high in both groups. The mean value of each predictor found in colMeans(x) is not informative or useful for prediction and often for purposes of interpretation, it is useful to center or scale each column. This can be achieved with the preProcess argument in train. Re-run LDA with preProcess = "center". Note that accuracy does not change, but it is now easier to identify the predictors that differ more between groups than based on the plot made in Q2.


```{r}
fit_lda <- train(x, y, method = "lda", preProcess = "center")
fit_lda$results["Accuracy"]
t(fit_lda$finalModel$means) %>% data.frame() %>%
	mutate(predictor_name = rownames(.)) %>%
	ggplot(aes(predictor_name, hippocampus)) +
	geom_point() +
	coord_flip()
```

You can see that it is different genes driving the algorithm now. This is because the predictor means change.

In the previous exercises we saw that both LDA and QDA approaches worked well. For further exploration of the data, you can plot the predictor values for the two genes with the largest differences between the two groups in a scatter plot to see how they appear to follow a bivariate distribution as assumed by the LDA and QDA approaches, coloring the points by the outcome, using the following code:

```{r}
d <- apply(fit_lda$finalModel$means, 2, diff)
ind <- order(abs(d), decreasing = TRUE)[1:2]
plot(x[, ind], col = y)
```


Which TWO genes drive the algorithm after performing the scaling?
OAZ2 & SPI1

## Q6
Now we are going to increase the complexity of the challenge slightly. Repeat the LDA analysis from Q5 but using all tissue types. Use the following code to create your dataset:


```{r}
library(dslabs)      
library(caret)
data("tissue_gene_expression")
           
set.seed(1993)
y <- tissue_gene_expression$y
x <- tissue_gene_expression$x
x <- x[, sample(ncol(x), 10)]
```


```{r}
fit_lda <- train(x, y, method = "lda", preProcess = c("center"))
fit_lda$results["Accuracy"]
```

We see that the results are slightly worse when looking at all of the tissue types instead of only selected ones. You can use the confusionMatrix function to learn more about what type of errors we are making, like this: confusionMatrix(fit_lda).

What is the accuracy using LDA?
Answer:0.819 