---
title: "Comprehension Check: Trees and Random Forests"
output: github_document
---

## Q1

Create a simple dataset where the outcome grows 0.75 units on average for every increase in a predictor, using this code:
Which code correctly uses rpart to fit a regression tree and saves the result to fit?

```{r}
library(rpart)
n <- 1000
sigma <- 0.25
set.seed(1)
x <- rnorm(n, 0, 1)
y <- 0.75 * x + rnorm(n, 0, sigma)
dat <- data.frame(x = x, y = y)
fit <- rpart(y ~ ., data = dat)
```

## Q2
Which of the following plots has the same tree shape obtained in Q1?

```{r}
plot(fit)
text(fit)
```

## Q3
Below is most of the code to make a scatter plot of y versus x along with the predicted values based on the fit.

```{r}
library(tidyverse)
dat %>% 
	mutate(y_hat = predict(fit)) %>% 
	ggplot() +
	geom_point(aes(x, y)) +
	#BLANK
  geom_step(aes(x, y_hat), col=2)
  #BLANK
```
Which line of code should be used to replace #BLANK in the code above?

## Q4
Now run Random Forests instead of a regression tree using randomForest from the __randomForest__ package, and remake the scatterplot with the prediction line. Part of the code is provided for you below.

```{r}
library(randomForest)
fit <- randomForest(y ~ x, data = dat)#BLANK 
dat %>% 
	mutate(y_hat = predict(fit)) %>% 
	ggplot() +
	geom_point(aes(x, y)) +
	geom_step(aes(x, y_hat), col = 2)
```
What code should replace #BLANK in the provided code?

## Q5

Use the plot function to see if the Random Forest from Q4 has converged or if we need more trees.

```{r}
plot(fit)
```
Which is the correct plot to assess whether the Random Forest has converged?


## Q6
It seems that the default values for the Random Forest result in an estimate that is too flexible (unsmooth). Re-run the Random Forest but this time with a node size of 50 and a maximum of 25 nodes. Remake the plot.

Part of the code is provided for you below.

```{r}
library(randomForest)
fit <- randomForest(y ~ x, data = dat, nodesize = 50, maxnodes = 25)#BLANK
dat %>% 
	mutate(y_hat = predict(fit)) %>% 
	ggplot() +
	geom_point(aes(x, y)) +
	geom_step(aes(x, y_hat), col = 2)
```
What code should replace #BLANK in the provided code?