---
title: "Visualizing Two Numeric Variables"
output: github_document
---

We are requested to answer these questions:

    1. How are runtime and box-office revenue related?
    2. Has the average box-office revenue changed over time?
    
    
*Bivariate Visualization for two quantitiative variables*
## Setting up environment

```{r}
movies <- read.csv('../data/Movies.csv')
main_label <- "Runtime vs. Box Office Revenue"
runtime_in_minutes_label <- "Runtime (minutes)"
box_office_label <- "Box Office ($M)"
density_label <- "Density"
```


## Plots

### Scatter plot

Create a scatterplot
```{r}
plot(
  x = movies$Runtime,
  y = movies$Box.Office,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)

```

**Create a linear regression model**

```{r}
model <- lm(movies$Box.Office ~ movies$Runtime)
```

Draw the linear regression line on the plot

```{r}
plot(
  x = movies$Runtime,
  y = movies$Box.Office,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)

lines(
  x = movies$Runtime,
  y = model$fitted,
  col = "red",
  lwd = 3)
```

*As we can see there is a weak correlation between the two variables.*

### Heatmap

Now we need to install the package hexbin `install.packages("hexbin")`. 

Now we load hexbin library

```{r}
library(hexbin)
```

Create a hexagonal binned frequency heatmap

```{r}
hexbin <- hexbin(
  x = movies$Runtime,
  y = movies$Box.Office,
  xbins = 30,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)

plot(
  x = hexbin,
  main = main_label)
```


### MASS Package

For the following plots we need to create a 2D kernel density estimate using MASS, to install it we execute `install.packages("MASS")`  

Now we load the library
```{r}
library(MASS)
```

Now create a 2D kernel density estimation

```{r}
density2d <- kde2d(
  x = movies$Runtime,
  y = movies$Box.Office,
  n = 50)
```

### Contour plot

Create a contour plot of density, as you can see for this scenario this visualizartion is not the best.
```{r}
contour(
  x = density2d$x,
  y = density2d$y,
  z = density2d$z,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label)
```


### Level plot of dentisty
Create a level plot of density, please note that this is not exactly the expected plot, but it close enough in the base library.

It is like density heatmap.
```{r}
image(x = density2d$x,
      y = density2d$y,
      z = density2d$z,
      col =topo.colors(100),
      main = main_label,
      xlab = runtime_in_minutes_label,
      ylab = box_office_label)
```


### Mesh plot of density

Create a mesh plot of density

```{r}
persp(
  x = density2d$x,
  y = density2d$y,
  z = density2d$z,
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label,
  zlab = density_label)
```

### Surface plot of density

Create surface plot of density
```{r}
palette(topo.colors(100))

persp(
  x = density2d$x,
  y = density2d$y,
  z = density2d$z,
  col = cut(density2d$z,100),
  main = main_label,
  xlab = runtime_in_minutes_label,
  ylab = box_office_label,
  zlab = density_label)
```

Reset the color palette to default
```{r}
palette("default")
```
### Load time series data

Load time series data
```{r}
timeSeries <- read.csv("../data/Timeseries.csv")
```

Display the time series data

```{r}
head(timeSeries)
```

### Step chart
Create a step chart

```{r}
plot(
  x = timeSeries,
  type = "s",
  ylim = c(0, max(timeSeries$Box.Office)),
  main = "Average Box Office Revenue by Year",
  xlab = "Year",
  ylab = "Box Office ($M)")
```


### Line chart

Create a line chart
```{r}
plot(
  x = timeSeries,
  type = "l",
  ylim = c(0, max(timeSeries$Box.Office)),
  main = "Average Box Office Revenue by Year",
  xlab = "Year",
  ylab = "Box Office ($M)")
```

### Area charts

Area charts are not easy to create on the base library, they will be included into lattice and ggplot exeamples.
