---
title: "Comprehension Check: Distance"
output: github_document
---


## Q1

Load the following dataset:

```{r}
library(dslabs)
data("tissue_gene_expression")
```

This dataset includes a matrix x:

```{r}
dim(tissue_gene_expression$x)
```


This matrix has the gene expression levels of 500 genes from 189 biological samples representing seven different tissues. The tissue type is stored in y:

```{r}
table(tissue_gene_expression$y)
```

Which of the following lines of code computes the Euclidean distance between each observation and stores it in the object d?

Answer:
```{r}
d <- dist(tissue_gene_expression$x)
```


## Q2

Compare the distances between observations 1 and 2 (both cerebellum), observations 39 and 40 (both colon), and observations 73 and 74 (both endometrium).

Distance-wise, are samples from tissues of the same type closer to each other?


```{r}
d_matrix <- as.matrix(d)
d_matrix[1:2,1:2]
d_matrix[39:40,39:40]
d_matrix[73:74,73:74]
```
Answer : 

Yes, the samples from the same tissue type are closest to each other


## Q3

Make a plot of all the distances using the image function to see if the pattern you observed in Q2 is general.
Which code would correctly make the desired plot?

```{r}
image(as.matrix(d))
#image(d_matrix)[order(tissue_gene_expression$y):order(tissue_gene_expression$y)]
```
