---
title: "Comprehension Check: Caret Package"
output: github_document
---

## Q1

In the exercise in Q6 from Comprehension Check: Trees and Random Forests, we saw that changing nodesize to 50 and setting maxnodes to 25 yielded smoother results. Let's use the train function to help us pick what the values of nodesize and maxnodes should be.

From the caret description of methods, we see that we can't tune the maxnodes parameter or the nodesize argument with randomForests. So we will use the __Rborist__ package and tune the minNode argument. Use the train function to try values minNode <- seq(25, 100, 25). Set the seed to 1.

Which value minimizes the estimated RMSE?

```{r}
library(randomForest)
library(Rborist)
library(dslabs)
library(rpart)
library(caret)
library(tidyverse)
n <- 1000
sigma <- 0.25
set.seed(1)
x <- rnorm(n, 0, 1)
y <- 0.75 * x + rnorm(n, 0, sigma)
dat <- data.frame(x = x, y = y)

grid <- data.frame(minNode = seq(25, 100 , 25), predFixed = 1)
fit <- train(y ~ ., method = "Rborist", tuneGrid = grid , data = dat )
ggplot(fit)

```

Answer: 50

## Q2

Part of the code to make a scatterplot along with the prediction from the best fitted model is provided below.

```{r}
library(caret)
dat %>% 
	mutate(y_hat = predict(fit)) %>% 
	ggplot() +
	geom_point(aes(x, y)) +
    #BLANK
  geom_step(aes(x, y_hat), col = 2)
```


Which code correctly can be used to replace #BLANK in the code above?


## Q3

Use the rpart function to fit a classification tree to the tissue_gene_expression dataset. Use the train function to estimate the accuracy. Try out cp values of seq(0, 0.1, 0.01). Plot the accuracies to report the results of the best model. Set the seed to 1991.

Which value of cp gives the highest accuracy?

```{r}
set.seed(1991)
data("tissue_gene_expression")
    
fit <- with(tissue_gene_expression, 
                train(x, y, method = "rpart",
                      tuneGrid = data.frame(cp = seq(0, 0.1, 0.01))))
    
ggplot(fit)       
```

Answer 0

## Q4
Study the confusion matrix for the best fitting classification tree from the exercise in Q3.

What do you observe happening for the placenta samples?
Answer: Placenta samples are being classified somewhat evenly across tissues.

Explanation:
confusionMatrix(fit) will show the confusion matrix for the classification tree from the tissue gene expression dataset. Looking at the confusion matrix, you can see that placenta is classified somewhat evenly across different tissue types, and in fact, placentas are called endometriums more frequently than they are called placentas.
```{r}
confusionMatrix(fit)
```


## Q5
Note that there are only 6 placentas in the dataset. By default, rpart requires 20 observations before splitting a node. That means that it is difficult to have a node in which placentas are the majority. Rerun the analysis you did in the exercise in Q3, but this time, allow rpart to split any node by using the argument control = rpart.control(minsplit = 0). Look at the confusion matrix again to determine whether the accuracy increases. Again, set the seed to 1991.

What is the accuracy now?
```{r}
set.seed(1991)
data("tissue_gene_expression")
control = rpart.control(minsplit = 0)
fit <- with(tissue_gene_expression, 
                train(x, y, method = "rpart",
                      tuneGrid = data.frame(cp = seq(0, 0.1, 0.01)),control = control))
    
ggplot(fit) 
```

```{r}
confusionMatrix(fit)
```
Answer Expected : 0.9141


## Q6

Plot the tree from the best fitting model of the analysis you ran in Q5.

Which gene is at the first split?

```{r}
plot(fit$finalModel)
text(fit$finalModel)
```

Answer: GPA33 

## Q7

We can see that with just seven genes, we are able to predict the tissue type. Now let's see if we can predict the tissue type with even fewer genes using a Random Forest. Use the train function and the rf method to train a Random Forest. Try out values of mtry ranging from seq(50, 200, 25) (you can also explore other values on your own). What mtry value maximizes accuracy? To permit small nodesize to grow as we did with the classification trees, use the following argument: nodesize = 1.

Note: This exercise will take some time to run. If you want to test out your code first, try using smaller values with ntree. Set the seed to 1991 again.

What value of mtry maximizes accuracy?
Answer 100

```{r}
set.seed(1991, sample.kind = "Rounding")
library(randomForest)
fit <- with(tissue_gene_expression, 
                train(x, y, method = "rf", 
                      nodesize = 1,
                      tuneGrid = data.frame(mtry = seq(50, 200, 25))))
    
ggplot(fit)
```

## 8
Use the function varImp on the output of train and save it to an object called imp.

```{r}
imp <- varImp(fit)#BLANK
imp
```
What should replace #BLANK in the code above?

## Q9
The rpart model we ran above produced a tree that used just seven predictors. Extracting the predictor names is not straightforward, but can be done. If the output of the call to train was fit_rpart, we can extract the names like this:

```{r}
tree_terms <- as.character(unique(fit$finalModel$frame$var[!(fit$finalModel$frame$var == "<leaf>")]))
tree_terms

```
Calculate the variable importance in the Random Forest call for these seven predictors and examine where they rank.

What is the importance of the CFHR4 gene in the Random Forest call? 35
What is the rank of the CFHR4 gene in the Random Forest call? 7
  
```{r}
data_frame(term = rownames(imp$importance), 
			importance = imp$importance$Overall) %>%
	mutate(rank = rank(-importance)) %>% arrange(desc(importance)) %>%
	filter(term %in% tree_terms)
```

