---
title: "Comprehension Check: Regularization"
output: github_document
---

The exercises in Q1-Q8 work with a simulated dataset for 100 schools. This pre-exercise setup walks you through the code needed to simulate the dataset.

An education expert is advocating for smaller schools. The expert bases this recommendation on the fact that among the best performing schools, many are small schools. Let's simulate a dataset for 100 schools. First, let's simulate the number of students in each school, using the following code:

```{r}
library(tidyverse)

set.seed(1986, sample.kind = "Rounding")
n <- round(2^rnorm(1000, 8, 1))
```

Now let's assign a true quality for each school that is completely independent from size. This is the parameter we want to estimate in our analysis. The true quality can be assigned using the following code:

```{r}
set.seed(1, sample.kind = "Rounding")
mu <- round(80 + 2*rt(1000, 5))
range(mu)
schools <- data.frame(id = paste("PS",1:100),
                      size = n,
                      quality = mu,
                      rank = rank(-mu))
```

We can see the top 10 schools using this code: 

```{r}
schools %>% top_n(10, quality) %>% arrange(desc(quality))
```

Now let's have the students in the school take a test. There is random variability in test taking, so we will simulate the test scores as normally distributed with the average determined by the school quality with a standard deviation of 30 percentage points. This code will simulate the test scores:

```{r}

set.seed(1, sample.kind = "Rounding")
scores <- sapply(1:nrow(schools), function(i){
       scores <- rnorm(schools$size[i], schools$quality[i], 30)
       scores
})
schools <- schools %>% mutate(score = sapply(scores, mean))

```


## Q1

What are the top schools based on the average score? Show just the ID, size, and the average score.

Report the ID of the top school and average score of the 10th school.

What is the ID of the top school? 67
What is the average score of the 10th school? 88.0949

```{r}
schools %>% arrange(desc(score)) %>% top_n(10)
```


## Q2
Compare the median school size to the median school size of the top 10 schools based on the score.

What is the median school size overall? 261
What is the median school size of the of the top 10 schools based on the score? 136

```{r}
class(schools)
schools %>%
  select(size) %>%
  summarise(size = median(.$size))


schools %>% arrange(desc(score)) %>% top_n(10) %>% summarize(size = median(size))

```


## Q3
According to this analysis, it appears that small schools produce better test scores than large schools. Four out of the top 10 schools have 100 or fewer students. But how can this be? We constructed the simulation so that quality and size were independent. Repeat the exercise for the worst 10 schools.

What is the median school size of the bottom 10 schools based on the score? 146


```{r}
schools %>% 
  arrange(score) %>% 
  top_n(-10) %>% 
  summarize(size = median(size))
```


## Q4

From this analysis, we see that the worst schools are also small. Plot the average score versus school size to see what's going on. Highlight the top 10 schools based on the true quality. Use a log scale to transform for the size.

What do you observe?
```{r}
schools %>% 
  ggplot(aes(x=score, y=size)) +
  geom_point() +
  geom_point(data = filter(schools, rank<=10), col=2)
  
```

We can see that the standard error of the score has larger variability when the school is smaller. This is a basic statistical reality we learned in PH125.3x: Data Science: Probability and PH125.4x: Data Science: Inference and Modeling courses! Note also that several of the top 10 schools based on true quality are also in the top 10 schools based on the exam score: schools %>% top_n(10, score) %>% arrange(desc(score)).

## Q5

Let's use regularization to pick the best schools. Remember regularization shrinks deviations from the average towards 0. To apply regularization here, we first need to define the overall average for all schools, using the following code:

```{r}
overall <- mean(sapply(scores, mean))
```

Then, we need to define, for each school, how it deviates from that average.

Write code that estimates the score above the average for each school but dividing by  n+α  instead of  n , with  n  the schools size and  α  a regularization parameters. Try  α=25 .

What is the ID of the top school with regularization? 91
What is the regularized score of the 10th school? 86.9007

```{r}
alpha <- 25
score_reg <- sapply(scores, function(x) overall + sum(x-overall)/(length(x)+alpha))
schools %>% mutate(score_reg = score_reg) %>%
  top_n(10,score_reg) %>% arrange(desc(score_reg))
  

```


## Q6
Notice that this improves things a bit. The number of small schools that are not highly ranked is now lower. Is there a better  α ? Find the  α  that minimizes the

$$
RMSE= \frac{1}{100} \Sigma_{i=1}^{100}(quality - estimate)^2
$$


What value of  α  gives the minimum RMSE? 128

```{r}
alphas <- seq(10,250)
rmse <- sapply(alphas, function(alpha){
	score_reg <- sapply(scores, function(x) overall+sum(x-overall)/(length(x)+alpha))
	mean((score_reg - schools$quality)^2)
})
plot(alphas, rmse)
alphas[which.min(rmse)]  
```

## Q7
Rank the schools based on the average obtained with the best  α . Note that no small school is incorrectly included.

What is the ID of the top school now? 91
What is the regularized average score of the 10th school now? 85.35335

```{r}
score_reg <- sapply(scores, function(x) overall+sum(x-overall)/(length(x)+128))
#score_reg <- mean((score_reg - schools$quality)^2)
schools %>% mutate(score_reg = score_reg) %>%
  top_n(10,score_reg) %>% arrange(desc(score_reg))


```

## Q8

A common mistake made when using regularization is shrinking values towards 0 that are not centered around 0. For example, if we don't subtract the overall average before shrinking, we actually obtain a very similar result. Confirm this by re-running the code from the exercise in Q6 but without removing the overall mean.

What value of  α  gives the minimum RMSE here? 

```{r}
alphas <- seq(10,250)
rmse <- sapply(alphas, function(alpha){
	score_reg <- sapply(scores, function(x) sum(x)/(length(x)+alpha))
	mean((score_reg - schools$quality)^2)
})
plot(alphas, rmse)
alphas[which.min(rmse)]  
```

