---
title: "Comprehension Check: Matrix Factorization"
output: github_document
---

## Q1

Load the tissue_gene_expression dataset. Remove the row means and compute the distance between each observation. Store the result in d.

Which of the following lines of code correctly does this computation?
```{r}
d <- dist(tissue_gene_expression$x - rowMeans(tissue_gene_expression$x)) correct
```

## Q2
Make a hierarchical clustering plot and add the tissue types as labels.

You will observe multiple branches.

Which tissue type is in the branch farthest to the left? Liver

## Q3
Run a k-means clustering on the data with  K=7 . Make a table comparing the identified clusters to the actual tissue types. Run the algorithm several times to see how the answer changes.

What do you observe for the clustering of the liver tissue?
Liver is classified in a single cluster roughly 20% of the time and in more than one cluster roughly 80% of the time. 

## Q4
Select the 50 most variable genes. Make sure the observations show up in the columns, that the predictor are centered, and add a color bar to show the different tissue types. Hint: use the ColSideColors argument to assign colors. Also, use col = RColorBrewer::brewer.pal(11, "RdBu") for a better use of colors.

Part of the code is provided for you here:
```{r}
library(RColorBrewer)
sds <- matrixStats::colSds(tissue_gene_expression$x)
ind <- order(sds, decreasing = TRUE)[1:50]
colors <- brewer.pal(7, "Dark2")[as.numeric(tissue_gene_expression$y)]
#BLANK
heatmap(t(tissue_gene_expression$x[,ind]), col = brewer.pal(11, "RdBu"), scale = "row", ColSideColors = colors)
```

