---
title: "Visualizing Two Categorical Variables"
output: github_document
---

We are requested to answer these questions:

    1. How many award-winning movies are in each rating category?
    2. What proportion of movies in each category have won awards?

Bivariate visualizations for two qualitiative variables

## Setup environment

Load data and create a contingency table
```{r}
movies <- read.csv("../data/Movies.csv")
awards <- table(movies$Awards,
                movies$Rating)
main_title <- "Count of Movies by Rating and Awards"
rating_title <- "Rating"
movies_title <- "Count of Movies"
print(awards)

```

## Bar Chart

### Grouped frequency bar chart

```{r}
barplot(
  height = awards,
  beside = TRUE,
  main = main_title,
  xlab = rating_title,
  ylab = movies_title,
  legend = c("No","Yes"),
  args.legend = list(
    x = "topleft",
    title = "Awards"))
```

### Stacked Frequency bar chart
Create a stacked frequency bar chart
```{r}
barplot(
  height = awards,
  main = main_title,
  xlab = rating_title,
  ylab = movies_title,
  legend =  c("No","Yes"),
  args.legend = list(
    x = "topleft",
    title="Awards"))
```

### 100% Stacked Frequency Bar Chart

Create a proportional Frequency table

```{r}
proportions <- apply(awards, 2, function(x){x /sum(x)} )
head(awards)
```

```{r}
head(proportions)
```


Create the bar chart.

```{r}
barplot(
  height = proportions,
  main = "Proportion of Movies by Rating and Awards",
  xlab = rating_title,
  ylab = "Proportion of Movies",
  legend = c("No","Yes"),
  args.legend = list(
    x = "topleft",
    title = "Awards"))
```


### Spine Plot
We need to swamp the rows and columns for this chart.

```{r}
awards <- table(
  movies$Rating,
  movies$Award)

colnames(awards) <- c("No", "Yes")

print(awards)
```

Create a spineplot
```{r}
spineplot(
  x = awards,
  main = "Proportion of Movies by Rating and Awards",
  xlab = rating_title,
  ylab = "Awards")

```

### Mosaic plot
Creating Mosaic plot

```{r}
mosaicplot(
  x = awards,
  main = "Proportion of Movies by Rating and Awards",
  xlab = rating_title,
  ylab = "Awards")
```


